Using either the same dataset(s) you used in the previous weeks’ exercise or a brand-new dataset of your choosing, perform the following transformations (Remember, anything you learn about the Housing dataset in these two weeks can be used for a later exercise!)
```{r}
library(readxl)
setwd("C:/Users/brean/OneDrive/Desktop/NucampFolder/projects/dsc520-1")
housing_data = read_excel("data/week-7-housing.xlsx")
print(housing_data)
```

Using the dplyr package, use the 6 different operations to analyze/transform the data - GroupBy, Summarize, Mutate, Filter, Select, and Arrange – Remember this isn’t just modifying data, you are learning about your data also – so play around and start to understand your dataset in more detail
```{r}
library(dplyr)

by_bedrooms <- housing_data %>% group_by(bedrooms)





```


Using the purrr package – perform 2 functions on your dataset.  You could use zip_n, keep, discard, compact, etc.
```{r}

```


Use the cbind and rbind function on your dataset
```{r}

```


Split a string, then concatenate the results back together

```{r}

```

