---
output:
  word_document: default
  html_document: default
---
Using either the same dataset(s) you used in the previous weeks’ exercise or a brand-new dataset of your choosing, perform the following transformations (Remember, anything you learn about the Housing dataset in these two weeks can be used for a later exercise!)
```{r}
library(readxl)
setwd("C:/Users/brean/OneDrive/Desktop/NucampFolder/projects/dsc520-1")
housing_data = read_excel("data/week-7-housing.xlsx")
print(housing_data)
```

Using the dplyr package, use the 6 different operations to analyze/transform the data - GroupBy, Summarize, Mutate, Filter, Select, and Arrange – Remember this isn’t just modifying data, you are learning about your data also – so play around and start to understand your dataset in more detail
```{r}
library(dplyr)

colnames(housing_data)[2] <- "sale_price"
colnames(housing_data)[14] <- "square_feet"
colnames(housing_data)[1] <- "sale_date"

bedrooms_group <- housing_data %>% group_by(bedrooms)
print(bedrooms_group)

year <- filter(housing_data, year_built == 1933)
print(year)

a <- housing_data %>% summarize(mean(bedrooms))
print(a)

c <- select(housing_data, square_feet, bedrooms, year_built, sale_price)
g <- select(housing_data, sale_date, ctyname, bath_full_count, sq_ft_lot)
print(c)

h <- c %>% mutate(price_per_sq = (sale_price / square_feet))
print(h)


d <- arrange(c, sale_price, year_built)
print(d)


```


Using the purrr package – perform 2 functions on your dataset.  You could use zip_n, keep, discard, compact, etc.
```{r}
library(purrr)
#f <- keep(housing_data, starts_with("s"))
#discard()

#housing_data %>% map(function(x) sum(x, na.rm=TRUE))

#f <- housing_data %>% keep(~ .$bath_full_count >= 2)

#f <- housing_data %>% keep(~ get_element(housing_data, "bath_full_count") >= 2)

#could not get keep to work for some reason??? if you know what I'm doing wrong, please let me know! 

f <- housing_data %>% mutate(sales = compact(sale_price))
n <- keep(housing_data$sale_price, ~.x > 100000)

print(f)
print(n)

#j <- c %>% discard(sitetype)
#could also not figure out discard

#print(j)

```


Use the cbind and rbind function on your dataset
```{r}
c_bind <- cbind(c,g)
#print(c_bind)
#removed these two print functions because it made my homework 500+ pages but they worked! 

new_row <- c("2170", "4", "1970", "730000")

r_bind <- rbind(c, new_row)
#print(r_bind)


```


Split a string, then concatenate the results back together

```{r}
library(stringr)

split_string <- str_split(string = year$ctyname, "&")
split_string2 <- str_split(string = year$sale_date, '&')
print(split_string)
print(split_string2)

paste_string <- paste(split_string, split_string2)
print(paste_string)


```

